Homework 5

### 2019-10-02 hw5/MSimonsHW5.tex
hw5
Correcting HW 5 number 1

\item To prove $\varphi_{\alpha}$ is closed under addition, first let $f$, $g$
be any elements of $S[x]$.  We know that $f+g$ is also an element of
$S[x]$ because the coefficients of $f$ and $g$ are elements of $S$, which is a
ring.  This implies that the coefficients of $f$ and $g$ are closed under
addition, so the coefficients of $f+g$ are also in $S$.
\\ \\
With this having be said, we can prove $\varphi_{\alpha}$ is closed under addition
as such:
\[
\varphi_{\alpha}(f+g) = (f+g)(\alpha) = f(\alpha) + g(\alpha)
= \varphi_{\alpha}(f) + \varphi_{\alpha}(g)
\]
We know $f \cdot g$ is an element of $S[x]$ since $S$ is closed under multiplication,
so the coefficients of $f \cdot g$ are elements of $S$.
\\ \\
We can prove $\varphi_{\alpha}$ is closed under multiplication as such:
\[
\varphi_{\alpha}(f \cdot g) = (f \cdot g)(\alpha) = f(\alpha) \cdot g(\alpha)
= \varphi_{\alpha}(f) \cdot \varphi_{\alpha}(g)
\]
Thus, $\varphi_{\alpha}$ is a ring homomorphism.

@@

\item TODO

>>>>

\item Assume that if $f(x)$, $g(x)$, $s(x)$, $d(x)$, $p(x)$ in $S[x]$ satisfy
\[
f(x) + g(x) = s(x)
\] \[
f(x) - g(x) = d(x)
\] \[
f(x)g(x) = p(x)
\]
then
\[
\] \[
f(\alpha) + g(\alpha) = s(\alpha)
\] \[
f(\alpha) - g(\alpha) = d(\alpha)
\] \[
f(\alpha)g(\alpha) = p(\alpha)
\]
We can prove that $\phi_{\alpha}$ is closed under addition as such:
\[
\phi_{\alpha}(f) + \phi_{\alpha}(g) = f(\alpha) + g(\alpha) = s(\alpha) = \phi_{\alpha}(s)
\] \[
\phi_{\alpha}(f) - \phi_{\alpha}(g) = f(\alpha) - g(\alpha) = d(\alpha) = \phi_{\alpha}(d)
\]
We can prove that $\phi_{\alpha}$ is closed under multiplication as such:
\[
\phi_{\alpha}(f)\phi_{\alpha}(g) = f(\alpha)g(\alpha) = p(\alpha) = \phi_{\alpha}(p)
\]
Thus, $\phi_{\alpha}$ is a ring homomorphism.

@@

\item Let $(a_0 + a_{1}x + ... + a_{n}x^n)$, $(b_0 + b_{1}x + ... + b_{n}x^n)$
be elements of $R_{1}[x]$.
\\
\\
We can prove $G$ is closed under addition as such:
\[
G((a_0 + a_{1}x + ... + a_{n}x^{n}) + (b_0 + b_{1}x + ... + b_{n}x^{n}))
\] \[
= G(a_0 + a_{1}x + ... + a_{n}x^n + b_0 + b_{1}x + ... + b_{n}x^{n})
\] \[
= F(a_{0}) + F(a_{1})x + ... + F(a_{n})x^{n} + F(b_{0}) + F(b_{1})x + ... + F(b_{n})x^{n}
\] \[
= (F(a_{0}) + F(a_{1})x + ... + F(a_{n})x^{n}) + (F(b_{0}) + F(b_{1})x + ... + F(b_{n})x^{n})
\] \[
= G(a_0 + a_{1}x + ... + a_{n}x^{n}) + G(b_0 + b_{1}x + ... + b_{n}x^{n})
\]
We can prove $G$ is closed under multiplication as such:
\[
G((a_0 + a_{1}x + ... + a_{n}x^{n}) (b_0 + b_{1}x + ... + b_{n}x^{n}))
\] \[
= G (a_{0}b_{0} + ... + a_{n}b_{m}x^{n+m})
\] \[
= F(a_{0}b_{0}) + ... + F(a_{n}b_{m})x^{n+m}
\] \[
= F(a_{0})F(b_{0}) + ... + F(a_{n})F(b_{m})x^{n+m}
\] \[
= (F(a_{0}) + F(a_{1})x + ... + F(a_{n})x^{n})(F(b_{0}) + F(b_{1})x + ... + F(b_{m})x^{m})
\] \[
= G(a_0 + a_{1}x + ... + a_{n}x^{n}) G(b_0 + b_{1}x + ... + b_{n}x^{n})
\]
Therefore $G$ is also a a ring homomorphism.
